### 2022-06-13 paper.tex
added hrules
reduced title spacing
add #of region explanation

To assess the impact of our methods on dimensionality reduction and the ability to distinguish different (sub)types of cells, we used a data set from \citet{luo2017single}. This data set consists of 3377 single-cell CpG methylomes from the murine frontal cortex, comprising 16 neuronal subtypes.
We subjected this data set to the standard scBS workflow: defining a set of genomic intervals, quantifying methylation in these intervals, and subjecting the resulting matrix to PCA.
We repeated this analysis several times, either using 100~kb windows or VMRs, and either using methylation fractions or mean shrunken residuals as a measure of methylation. \todo{Is the following correct?} For both types of regions, the 100~kb windows and the VMRs, we ranked the regions by the number of covering cells (i.e., cells with at least on read in the region) and kept only the top 100, 1000, or 10,000 regions.

@@

>>>>

To assess the impact of our methods on dimensionality reduction and the ability to distinguish different (sub)types of cells, we used a data set from \citet{luo2017single}. This data set consists of 3377 single-cell CpG methylomes from the murine frontal cortex, comprising 16 neuronal subtypes.
We subjected this data set to the standard scBS workflow: defining a set of genomic intervals, quantifying methylation in these intervals, and subjecting the resulting matrix to PCA.
We repeated this analysis several times, either using 100~kb windows or VMRs, and either using methylation fractions or mean shrunken residuals as a measure of methylation. 
For both types of regions, we varied the number of input regions, ranging from 100 to 50,000 high-coverage regions that were selected for PCA.
Specifically, we ranked regions by their number of coverging cells (i.e., cells with at least on read in the region) and selected those with the highest number.

@@

\vspace{1.6ex}
\noindent\hfil\rule{.6\columnwidth}{.2pt}\hfil
